\section{Future Works}
\label{future_works}

Working on this project led us to figure out new features that could be 
implemented in the future. In particular, one of these could be host migration: 
at the host disconnection, one of the slave devices could be elected (sorting it 
by MAC address or by username) as a new master and reinstantiate the match. 
By the way, this feature is not trivial to achieve since Bluetooth API in 
Android requires the user intervention, making the transition not seamless.

Another future work that we think it might be useful could be implementing 
the hot-join feature, allowing new players to join an already started match. 
One concern is regarding battery consumption though: keeping a Bluetooth device 
always discoverable is energy-consuming and it could drain the master battery 
very quickly. Nonetheless, Android documentation heavily discourage keeping a 
device discoverable, since it could be susceptible to security 
attacks\footnote{Additional documentation con be found at: \url{ 
https://developer.android.com/guide/topics/connectivity/bluetooth.html\#Enabling
Discoverability}}.
A fairly reasonable solution could be to give to the host the possibility to 
make his device discoverable.

Finally, the application could better support card games like Poker adding the 
possibility to retrieve all the money from the bank and the ability to see 
how much money a player has, thus making it more general purpose. Generally 
speaking, this extends the opportunities to use GameBank in different scenarios, 
especially in context not foreseen by us.