\section{Introduction}
\label{introduction}
% no \IEEEPARstart

Playing games can be a social activity, especially when playing board ones. 
Sometimes, though, the engagement can be reduced by the burden of managing the 
game itself by a master, a player that has to take in consideration the actions 
of everyone and act accordingly to the game mechanics. Recently a new concept 
of gaming, called pervasive gaming, is emerging. This concept merges the 
opportunities of the digital world with a physical one~\cite{arango17}. The 
most famous example of this is the mobile game Pokémon Go, published by 
Nintendo that is continuing to develop this concept with the Nintendo Labo 
project: a physical extension for Nintendo Switch console.
The virtualization improves the gameplay, making it easier to manage, even if 
there is always the need of a master~\cite{bjork01}.
For some activities, this role can be distributed to the members, spreading its 
duty to everyone. An example of this activity could be the one where there are 
transaction of in-game money. The distribution of this task can be performed in 
the same way Blockchain works: every member can emit a transaction and all the 
other peers have the possibility to check it and to determine its 
validity~\cite{nakamoto08}. This open up to a whole new type of possibilities, 
where new technologies, implemented as pervasive games, could be tested to real 
use cases.

Most of the time, players are located in the same room when playing board 
games. This particular scenario makes an already established technology in 
the market, Bluetooth, an optimal solution to implement pervasive applications. 
In our report, we will talk about GameBank, an example of pervasive game that, 
thanks to this wireless link, allow players to distribute the role of a Bank in 
monopoly-like games with a piconet.
Bluetooth, a technology developed initially by Ericsson, Nokia, IBM, Toshiba, 
Intel and many others~\cite{haartsen00}, has become today a widely used
standard especially in PAN (Personal Area Network) communications. This
wireless link has been chosen in GameBank for different reasons. First of all,
this protocol, being around for many years is known to most of the people,
making our application easier for the average user. Secondly, Bluetooth can
coexist with other protocols, and can handle interferences coming from other
signals (i.e. from WiFi). Battery consumption must be taken in consideration 
too, Bluetooth in the field of wireless communications has been proven to be 
one of the most battery-friendly radio technology~\cite{lee07}.

Finally, establishing the connection via Bluetooth
allows other wireless link to be used for other purposes, thus enabling the
user to perform other actions while playing our game, e.g. browsing the
internet via WiFi.\\

This paper is organised as follows: Section~\ref{introduction} describes how 
pervasive games and distribution of mastering duties can improve the overall 
gameplay, while Section~\ref{related_works} provides related works. 
Section~\ref{game_bank} describes how the application is designed and 
implemented, listing the problems we faced while developing it. At the end, in 
Section~\ref{results} we analyse some metric results about Bluetooth and in 
Section~\ref{future_works} we propose some future developments for our 
application. Finally, Section~\ref{conclusions} provides conclusions about our 
work.
